---
title: How is Chelsea Doing?
execute:
  echo: FALSE
---

The fortunes of a Premier League team rely heavily on their success in the transfer market, as can be seen with Chelsea FC, with their disastrous season. How much of an outlier was that season though? Data was taken from the 2021/22 and 2022/23 Premier League tables and the site Transfermarkt. The difference in points between the teams that were in the Premier League for both seasons was then calculated, alongside their balance of transactions during the period. I then estimated a posterior probability distribution with the transfer market balance as the independent variable and the change in points as the dependent variable. It showed that if you spend like Chelsea did in the transfer market, there is a 75.9% (plus or minus 2%) chance you suffer a loss in points, with the average loss being around 10.

```{r}
#| label: libraries
library(ggthemes)
library(knitr)
library(readr)
```

```{r}
#| label: expenditure vs points
main_plot <- read_rds(file = "pt_change_plot.rds")
main_plot
```
